\documentclass{article}
\oddsidemargin 0.1in
\addtolength{\oddsidemargin}{-.7in}
\addtolength{\textwidth}{3in}
\addtolength{\textheight}{2in}
\addtolength{\headheight}{-1in}
%\pagestyle{empty}
\begin{document}
\begin{center}
\textbf{
  Model Engineering College 
\\Department of Computer Engineering
\\B. Tech. Computer Science \& Engineering
\\CS492 Project
\\Periodic Report No.1 (For the period 14-03-2021 to 20-03-2021)
\\Copyright Protection and Violation Detection Using Blockchain
\\11 Ardra Mohan
\\31 Malavika Rajesh Vikraman
\\51 Sandra Jacob
\\52 Sanjana S}
\end{center}

\section{Work Assigned}
\begin{itemize}
\item Frontend for login and register using React.js.
\item Watermarking of images.
\item Backend for users to store their authentication credentials.
\item Blockchain environment setup.
\item Image uploading and storing in folder.
\item Setting up IPFS storage for the system.
\item Integrating PHash algorithm to site. 
\end{itemize}

\section{Work Done}
\begin{itemize}
\item Frontend for login and register using React.js.
\item Watermarking of images.
\item Backend for users to store their authentication credentials.
\item Blockchain environment setup.
\item Image uploading and storing in folder.
\item Setting up IPFS storage for the system.
\item Developed PHash algorithm.
\end{itemize}

\section{Work Schedule for Next 7 Days}
\begin{itemize}
\item Linking React.js pages with the database.
\item Implementing similarity detection algorithm.
\item Implementing smart contract for copyright.
\end{itemize}

\section{Assessment - Internal Guide}
Performance assessment \& Remarks by the internal guide: Poor/Acceptable/Satisfactory/Good/Very Good/Excellent
\vspace{1in}
\begin{tabbing}
	xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx\= xxxxxxxxxxxxxxxxxx\= \kill
\vspace{.1in}\\	
\textbf{Project Guide :} Mrs. Sony P  \>  \hspace{1.5in}\textbf{Project Coordinator:} Dr. Preetha Theresa Joy\\
        	   Assistant Professor(Dept. of Computer Engineering)\hspace{.5in} 	\> \hspace{1.5in}HOD(Dept. of Computer Engineering)\\

\end{tabbing}
\vspace{.1in}

\end{document}





